\section{Conclusions}

In this work only few topics related with launch pad and rocket security was covered.
Both aspects are very important in terms of the global safety of the facility and
need to be taken into account during the design phase of a launch pad. Both of them
helps to reduce risk of failure of space missions, that may cost hundreds of million
euros.

In the case of lightning protection it is proved that it actually prevents the
rocket to be hit by electric discharges, and it has been checked that almost
every launch pad analysed used some kind of active protection against electrical
lightnings. It has been showed that the purpose of that protection is not only
diverge or safely attract electric arcs, but also it's important for make the
volume where the rocket is placed, free of electromagnetic fields, what also can
develop undesired currents inside the rocket and the payload. Furthermore,
some intense electromagnetic fields could affect negatively instruments or electrical
devices inside the rocket, or in the launch pad itself, for example magnetometers,
gyroscopes.

That system also prevents the rocket to generate possible sparks between conductor
materials within the rocket, that could dramatically increase the risk of having
a ignition of the propellant and eventual explosion.

The other topic on acoustic protection of the launch pad has also been proven to be
effective by reducing the total amount of vibrations in some decibels, what is
always desired. The water used in deluge of the launch pad has the effect of absorbing
the huge air vibrations and also reduces the formation of steady waves modes within
the volume of plume deflector. It helps reducing the reflect shockwave with the ground
and other solid surfaces, that could damage the engines, or the nozzles, but also,
some launch pad structures.

After the study, it has been observed that there's a lot of work to do around launch
pads in terms of the security and also that there's a lot of things to study and improve.
Regarding the lightning protection it's still way to better understand the physics
underlying electric discharges in the atmosphere, maybe using computational techniques,
in order to better predict how to design lightning rods and towers in a efficient,
cheap manner.
