\begin{abstract}
This document contents the PDR report of the design of a future cubesat mission
developed by students of the Universitat Politecnica de Catalunya (UPC), during
the course 2018/19 as a part of the subject \textit{Spacecraft Design}.

To benefit the lives of people around the world, this project aims to develop
IoT communications. It is essential to implement a fast, global satellite network.
The proposed project will create a constellation of CubeSats to satisfy this need.

\end{abstract}

\section*{Acronyms list}

\begin{itemize}
	\small
	\setlength\itemsep{0cm}
	\item \textbf{ACDS}. Attitude Determination and Control System.
	\item \textbf{CDH}. Command and Data Handling subsystem.
	\item \textbf{COMM}. Communications subsystem.
	\item \textbf{DEP}. Deployment requirement.
	\item \textbf{ENV}. Environmental systems.
	\item \textbf{EPS}. Electrical Power Subsystem.
	\item \textbf{IoT}. Internet of Things.
	\item \textbf{MIS}. Mission requirement.
	\item \textbf{OBC}. On-Board Computer.
	\item \textbf{P/L}. Payload.
	\item \textbf{PDR}. Preliminary Design Review.
	\item \textbf{PM}. Project Manager.
	\item \textbf{PRP}. Propulsion subsystem.
	\item \textbf{PRR}. Preliminary Requirements Review.
	\item \textbf{PTL}. Project Technical Leader.
	\item \textbf{S/C}. Spacecraft.
	\item \textbf{SS}. Subsystem.
	\item \textbf{STR}. Structure subsystem.
	\item \textbf{SYS}. System requirement.
	\item \textbf{TBC}. To be checked.
	\item \textbf{TBD}. To be decided.
	\item \textbf{THC}. Thermal Control subsystem.
\end{itemize}

\newpage
\section{Introduction}

\MissionName is a CubeSat proposed mission that aims to deploy a network of small,
low-cost nanosatellites in orbits around the whole Earth in order to provide
citizens with an accessible, reliable Internet of Things, so they and their devices,
like, for example, intelligent cars, home appliances, shops, offices and homes, can
connect each other to interact and send information, make monetary transactions or
have remote control on the "Things" you may want to command.

The Internet of Things (IoT) is new emerging technology that is still open to many
possibilities and development. IoT is said to born during the beginnings of 2010 decade,
and it could have many applications in fields as different as consumer focus technologies
as smart home or elder care, or more commercial applications related with healthcare
(remote medical assistance, medical monitoring), transportation (smart traffic control,
emerging intelligent self-driven cars), building and home automation tasks for both
public, private or industrial applications; and also industrial applications like
manufacturing, with emerging big data technologies or by controlling supply chain
networks with a large number of distributed sensors; agriculture control or environmental
monitoring.

Companies and people are just starting to benefit from this emerging technology,
but the future possibilities are wide open, and there are many start-ups
entering to the market in the last few years. Our intent with this project is
to provide this technology from space, wherever you are in the planet, 24/7, with
the low-cost alternative of CubeSats, instead of heavier and more expensive
traditional satellites.

\section{Mission approach}
We propose a constellation of LEO CubeSats that will allow the communication between devices
connected to the IoT network, 24 hours a day. The information would travel from one
device to another through the constellation on satellites, ground stations and third party
satellites in near real time.

\section{Mission primary objective}

To design and implement a constellation of CubeSats which will provide global communications coverage

\section{Subsystems definition}
