\section{Project organization and schedule}

The project of designing a cubesat is not an easy task because it involves a
wide number of sciences and required knowledge and they must collaborate in
order to find the best solution (or at least, a good enough solution), for the
problems that would appear during the design phase.

In the case of satellites and spacecrafts, the sciences and field of knowledge
involved use to be: electronics, tele-communications, thermodynamics, mechanical
physics, astrodynamics. That means that is always interesting having a team with
a background in several areas of knowledge, so they may be able to solve the problems
better if they collaborate with his different points of view.

A typical satellite design is usually divided into subsystems, the one that were
already mention during this report. They are parts of the satellite that are
somehow independent, but also they may have important influences and dependencies
between them.

The team is also divided along with this subsystems, so each engineer could focus in
his area of knowledge. But, in the same way the subsystems should interact with each
other, the team members should do the same in order to understand the mutual influences.
It's also important having someone who keeps this organization, facilitate the
communications between the team members and be aware of the main problems and
relations between subsystems. This is what we called the "\textit{Project Technical Leader}" (PTL),
who would be the person in charge of helping the resolution of problems between
subsystems, improve the communications between them, know the main requirements of
the mission and follow the overall progress of the design. Also important is on
person in charge of the scheduling, and the distribution of work
and effort within the engineers, that is called the "\textit{Project Manager}" (PM).

In our case, this organization is as follows:

\begin{itemize}
	\item \textbf{Project Manager:} Carlos Molina
	\item \textbf{Project Technical Leader:} Jaspar Meister
	\item Subsystem responsibles:
	\begin{itemize}
		\item \textbf{ADCS:} Brad Gregory
		\item \textbf{STR:} Alvaro Boix
		\item \textbf{PRP:} Murrough Murnaghan
		\item \textbf{CDH:} Jaspar Meister
		\item \textbf{COMM:} Carlos Molina
		\item \textbf{EPS:} Anne-Laure Debrit
		\item \textbf{THC:} Thomas Barsch
		\item \textbf{ENV:} Justus Schuberth
	\end{itemize}
	\item \textbf{Media:} Justus Schuberth. In charge of the artist's impressions of the cubesat made with Blender.
\end{itemize}
